Digital History in Finland, 1488-1828

### 2016-07-11 inst/examples/manuscript-krakow.Rmd
Update manuscript-krakow.Rmd

  # PAPER CONSUMPTION
  theme_set(theme_bw(20))
  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
       geom_bar(aes(fill = language), position = "stack", stat = "identity") +              
       xlab("Publication year") +
       ylab("Paper consumption") +
       ggtitle(paste("Paper (", paste(sel, collapse = ";"), ")", sep = ""))
  print(p)
```

>>>>

  # PAPER CONSUMPTION
  theme_set(theme_bw(20))
  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
       geom_bar(aes(fill = language), position = "stack", stat = "identity") +              
       xlab("Publication year") +
       ylab("Paper consumption") +
       ggtitle(paste("Paper (", paste(sel, collapse = ";"), ")", sep = ""))
  print(p)
```
---

[Publishers in Sweden and Turku]

### Rock Bottom of the Great Northern War (1700-1721)

Publisher title count changes around 1700 with a nearly detrimental drop in Turku, significant publishing place in Finland at the time.

```{r drop1700B, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=7}
# https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/drop1700B-1.png

catalogue <- "Fennica"
place <- "Turku"

theme_set(theme_bw(20))
p <- ggplot(npub, aes(x = publication_year, y = n, group = publisher)) +
       geom_point(size = 5, aes(shape = publisher, color = publisher)) +
       geom_smooth(col = "black", aes(shape = publisher, fill = publisher, color = publisher)) + 
       xlab("Publication year") +
       ylab("Title count (n)") +
       ylim(c(0, 1.1*max(npub$n))) +
       ggtitle(paste("Title count (", place, "/", catalogue, ")", sep = ""))
print(p)
```
